Turkey Hemorrhagic Enteritis Virus transcriptome profiling

### 2023-03-17 README.Rmd
Update project README

---
title: Turkey Hemorrhagic Enteritis Virus transcription profiling
author: Abraham Quaye
date: 2023-03-16
output: html_document
---

# THEV transcriptome studies

@@

![project_map](./project_map.svg){width=620px height=480px}

@@

`r script_dir`

>>>>

---
title: Turkey Hemorrhagic Enteritis Virus transcriptome profiling
author: Abraham Quaye
date: 2023-03-16
output: html_document
---
```{css echo=FALSE}
body {
    font-size: 2vw
}
```
<!-- # THEV transcriptome studies -->

@@

![project_map](./project_map.svg){width=920px height=680px}

@@
